Marginally-Stable Thermal Equilibria of Rayleigh-Bénard Convection

### 2021-04-16 publication_materials/ms_rbc.tex

\section{Properties of Thermally Equilibrated States}\label{sec:properties}
MSTE are fixed points of the quasilinear form derived in section \ref{sec:model}, differing from ECS in that ECS are fixed points of the full nonlinear problem \eqss{EQ:motion1}{EQ:motion3}. 
Such definitions are not mutually exclusive, but in general we can assume that MSTE and ECS are not steady with respect to their counterparts' problems.
We compute symmetric MSTE for $Ra$ in the range $10^5 - 10^9$.

@@

Figure \ref{fig:T0_profiles} gives temperature profiles for $\Ra = 10^8$ where the initial profile, whose construction is outlined in \ref{sec:initial_profile}, is employed at iteration 0. 
DNS (direct numerical simulations) are performed by solving \eqss{EQ:motion1}{EQ:motion3} with \texttt{Dedalus}, followed by horizontal- and time- averaging. 
The DNS curve is more diffuse than the MSTE curve, which in turn, is more diffuse than the initial curve. 
Performing an eigenvalue solve by setting $\bar{T}$ equal to the DNS profile yields positive eigenvalues. 
Comprehensively, this suggests that MSTE might maximize boundary layer thickness, while subject to the marginal stability constraint.

@@

\section*{Appendix}
\subsection{Initial buoyancy profile} \label{sec:initial_profile}
We initialize the thermal-equilibration algorithm with \cite{Shishkina}'s analytical thermal boundary layer equation for turbulent Rayleigh-B\'enard convection, given by 
\begin{align}
    \bar{T}_0(\xi) &= \frac{\sqrt{3}}{4\pi} \log \frac{(1 + a\xi)^3}{1 + (a\xi)^3} + \frac{3}{2\pi} \arctan \Big( \frac{4\pi}{9}\xi - \frac{1}{\sqrt{3}} \Big) + \frac{1}{4} \nonumber \\
    \xi &= \frac{z}{\delta_0}, \qquad a = \frac{2\pi}{3\sqrt{3}}\label{EQ:T0}
\end{align}
where $\delta_0$ is the boundary layer height. 
We expect that each $\Ra$ is associated with a unique $\delta_0$ for which $\bar{T}_0(z)$ is marginally-stable. 
It should be noted that when experimenting with various initial profiles $(\tanh, \rm{erf}, \rm{etc.})$, we obtain indistinguishable equilibrated states, implying that solutions may be unique. 
An example of \eq{EQ:T0} is given by the blue curve in Figure \ref{fig:T0_profiles}.

>>>>

\section{Properties of Thermally Equilibrated States}\label{sec:properties}
We evolve $\bar{T}$ as described above until $\partial_t\bar{T}\approx 0$ \note{what is your criterion for equilibrium?}.
In this marginally-stable thermal equilibrium, $\bar{T}$ does not evolve in time, and the perturbations also do not evolve in time, as they are marginally stable.
Thus, these configurations are exact solutions to the quasilinear equations (equations~\ref{EQ:T0_IVP}--\ref{EQ:linear3}).
They differ from the usual ECS in that ECS are fixed points of the full nonlinear problem (\ref{EQ:motion1})--(\ref{EQ:motion3}). 
Such definitions are not mutually exclusive, but in general we can assume that MSTE and ECS are not steady with respect to their counterparts' equations.
We compute symmetric MSTE for $Ra$ in the range $10^5 - 10^9$ \note{Somewhere you need to state we impose symmetry on the temperature field... this should got in section 3}.

@@

Figure \ref{fig:T0_profiles} gives temperature profiles for $\Ra = 10^8$ where the initial profile, whose construction is outlined in \ref{sec:initial_profile}, is employed at iteration 0. 
DNS (direct numerical simulations) are performed by solving \eqss{EQ:motion1}{EQ:motion3} with \texttt{Dedalus}, followed by horizontal- and time- averaging. 
The DNS curve is more diffuse than the MSTE curve, which in turn, is more diffuse than the initial curve. 
Performing an eigenvalue solve by setting $\bar{T}$ equal to the DNS profile yields positive eigenvalues. 
This suggests that MSTE might maximize boundary layer thickness, while subject to the marginal stability constraint.

@@

\section*{Acknowledgments}
The authors thank Geoff Vasil, Greg Chini, and Emma Kaufman for their valuable feedback and suggestions. 
We also thank the \texttt{Dedalus} and \texttt{Eigentools} development teams. 
Computations were performed on the NASA Pleiades system.

\appendix

\section{Initial buoyancy profile} \label{sec:initial_profile}
We initialize the thermal-equilibration algorithm with \cite{Shishkina}'s analytical thermal boundary layer equation for turbulent Rayleigh-B\'enard convection, given by 
\begin{align}
    \bar{T}_0(\xi) &= \frac{\sqrt{3}}{4\pi} \log \frac{(1 + a\xi)^3}{1 + (a\xi)^3} + \frac{3}{2\pi} \arctan \Big( \frac{4\pi}{9}\xi - \frac{1}{\sqrt{3}} \Big) + \frac{1}{4} \nonumber \\
    \xi &= \frac{z}{\delta_0}, \qquad a = \frac{2\pi}{3\sqrt{3}}\label{EQ:T0}
\end{align}
where $\delta_0$ is the boundary layer height. 
We expect that each $\Ra$ is associated with a unique $\delta_0$ for which $\bar{T}_0(z)$ is marginally-stable. 
It should be noted that when experimenting with various initial profiles $(\tanh, \rm{erf}, \rm{etc.})$, we obtain indistinguishable equilibrated states, implying that solutions may be unique. 
An example of \eq{EQ:T0} is given by the blue curve in Figure \ref{fig:T0_profiles}.
